---
title: "Weight of Fish"
author: "Kimberly Aldana"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

### Best Models


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```


### Best Two regressor model

Best two regression models are height and width.


```{r}
Perchmodel <- lm(Weight~Height+Width, data = Perch)
summary.lm(Perchmodel)
```

The residual standard error is 85.17. The adjusted R squared is 0.94. With a p value of 2.2e - 16.


## Pike

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

L1 and L3 are the two best regression models. Best regression model is everything.


### Best Models

```{r}
Pikebest <- lm(Weight~., data = Pike)
summary.lm(Pikebest)
```

The residual standard error is 70.86. The adjusted R squared is 0.9794. The p value is 8.679e-10.


### Best Two regressor model

```{r}
Piketwo <- lm(Weight~Length1+Length3, data = Pike)
summary.lm(Piketwo)
```

The residual standard error is 92.56. The adjusted R squared is 0.9649. The p value is 2.572e-11.This summarizes our best two regression models.



## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements